\textbf{Photovoltaic System Reconfiguration strategy for mismatch condition}

### 2018-08-06 test/main.tex
20180806

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{subcaption}
\usepackage[sorting=none]{biblatex}
\addbibresource{biblio.bib}
\usepackage{amsmath}
\usepackage{esint}
\usepackage{systeme}
\usepackage{algorithm2e}
\usepackage{blindtext}
\usepackage{subcaption}
\usepackage{minted}
\usepackage{stackengine}
\usepackage[a4paper,margin=0.5in]{geometry}
\title{\textbf{Photovoltaic System Reconfiguration strategy for mismatch condition}}%\\
           %\emph{Application to mixed typed of data in lung Adenocarcinoma subtype discovery}}
\date{July 2018}
\author{\textbf{Dafang Zhao}\\Nara Institute of Science and Technology, Depenadble System Lab}

@@

\section{Introduction}
\\As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human. Photovolatic (PV) energy recived signifcant attention since it has unlimited energy and easy to be scaled up.

>>>>

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{subcaption}
\usepackage[sorting=none]{biblatex}
\addbibresource{biblio.bib}
\usepackage{amsmath}
\usepackage{esint}
\usepackage{systeme}
\usepackage{algorithm2e}
\usepackage{blindtext}
\usepackage{subcaption}
\usepackage{minted}
\usepackage{stackengine}
\usepackage[a4paper,margin=0.5in]{geometry}
\title{\textbf{Photovoltaic System Reconfiguration strategy for mismatch condition}}%\\
           %\emph{Application to mixed typed of data in lung Adenocarcinoma subtype discovery}}
\date{July 2018}
\author{\textbf{Dafang Zhao}\\Nara Institute of Science and Technology, Dependable System Lab}

@@

\section{Introduction}
\\As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human. Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up. Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
